---
title: "Differential expression analysis--MAST cpm det mode"
author: "Siming Zhao"
date: "2019-03-25"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval=T, message=FALSE)
```
MAST cpm det mode from https://github.com/csoneson/conquer_comparison/blob/master/scripts/apply_MASTcpmDetRate.R.

Load functions and setup
```{r loadfunc, eval=T}
source("code/summary_functions.R")
source("code/DE_functions.R")
library(dplyr)
library(gtools)
library(data.table)
load("data/DE_input.Rd")

displayout <- function(res){
 summ_pvalues(res$pval)
 print(paste0("There are ",dim(res[res$fdr < 0.1,])[1], " genes passed FDR <0.1 cutoff"))
 print(knitr::kable(signif(as.matrix(head(res)),digit=2)))
}
```

Load data for a particular locus
```{r locusdata, eval=T}
glocus <- "VPS45"
Nperm <- 5
gcount <- dm[1:(dim(dm)[1]-76), colnames(dm1dfagg)[dm1dfagg[glocus,] >0 & nlocus==1]]
ncount <- dm[1:(dim(dm)[1]-76), colnames(dm1dfagg)[dm1dfagg["neg",] >0 & nlocus==1]]
```

Load data for a particular gRNA
```{r gRNAdata, eval=F, include=F, echo=F}
gRNA <- "VPS45_1_gene"
genedm <- dm[1:(dim(dm)[1]-76), ]
gRNAdm0 <- dm[(dim(dm)[1]-75):dim(dm)[1],]
gRNAlocus <- strsplit(gRNA, split = "_")[[1]][1]
gcount <- genedm[,gRNAdm0[gRNA,] >0 & colSums(gRNAdm0[rownames(gRNAdm0) != gRNA,]) ==0]
if (dim(gcount)[2] !=0 & gRNAlocus != "neg") {
    ncount1 <- genedm[, colnames(dm1dfagg)[dm1dfagg["neg",] >0 & nlocus==1]]
    ncount2 <- genedm[, colnames(dm1dfagg)[dm1dfagg[gRNAlocus,] == 0]]
}
ncount <- ncount1
```

## Run MAST--No filtering
```{r }
y <- DE_process(gcount, ncount, filtcpm=-1, filtpercent=0.2, perm=F)
res <- run_MASTcpmDetRate(y)
displayout(res)
```

### Permutation
```{r }
for (n in 1:Nperm){
  y <- DE_process(gcount, ncount, filtcpm=-1, filtpercent=0.2, perm=T)
  res <- run_MASTcpmDetRate(y)
  displayout(res)
}
```

## Run MAST-- filtering cpm > `r filtcpm=0; filtcpm` in more than `r filtpercent=0.03;filtpercent` cells
```{r }
y <- DE_process(gcount, ncount, filtcpm=filtcpm, filtpercent=filtpercent, perm=F)
res <- run_MASTcpmDetRate(y)
displayout(res)
```

### Permutation
```{r }
for (n in 1:Nperm){
  y <- DE_process(gcount, ncount, filtcpm=filtcpm, filtpercent=filtpercent, perm=T)
  res <- run_MASTcpmDetRate(y)
  displayout(res)
}
```

## Run MAST-- filtering cpm > `r filtcpm=0; filtcpm` in more than `r filtpercent=0.2;filtpercent` cells
```{r }
y <- DE_process(gcount, ncount, filtcpm=filtcpm, filtpercent=filtpercent, perm=F)
res <- run_MASTcpmDetRate(y)
displayout(res)
```

### Permutation
```{r }
for (n in 1:Nperm){
  y <- DE_process(gcount, ncount, filtcpm=filtcpm, filtpercent=filtpercent, perm=T)
  res <- run_MASTcpmDetRate(y)
  displayout(res)
}
```

## Parameters used
* We used data processed after QC step [here](Quality_metrics.html).  
* targeted locus, choose `r glocus`. 
